---
title: "R Notebook"
output: html_notebook
Author: "Bharat Simha Reddy, Sahith Reddy"
---


"Question-1"

#Question-1 : Find the distribution of how many times a pair users (i.e., address1 and address2) 1 - buys, 2 - sells a token with each other. Which distribution type fits these distributions best? Estimate population distribution parameters.

```{r}
library(dplyr)
library(fitdistrplus)
library(UsingR)
```

##Preprocessing
```{r}

mcap <- read.table('networkmcapTX.txt', sep=" ")
statusnetwork <- read.table('networkstatusnetworkTX.txt', sep=" ")
bnb <- read.table('networkbnbTX.txt', sep=" ")

```

```{r}
names(mcap) <- c('SellerInfo', 'BuyerInfo', 'TimeStamp', 'TokenPrice')
names(statusnetwork) <- c('SellerInfo', 'BuyerInfo', 'TimeStamp', 'TokenPrice')
names(bnb) <- c('SellerInfo', 'BuyerInfo', 'TimeStamp', 'TokenPrice')
```

```{r}
supply_mcap <- 100000000
supply_statusnetwork <- 6804870174.8781
supply_bnb <- 183345602.24249
decimals_mcap <- 10^8
decimals_statusnetwork <- 10^18
decimals_bnb <- 10^18
```

```{r}
mcapFiltered <- mcap %>% filter(TokenPrice < decimals_mcap* supply_mcap)
statusnetworkFiltered <- statusnetwork %>% filter(TokenPrice < decimals_statusnetwork * supply_statusnetwork)
bnbFiltered <- bnb %>% filter(TokenPrice < decimals_bnb* supply_bnb)
```

##Checking Outliers
```{r}
nrow(mcap)
nrow(mcapFiltered)
mcap %>% filter(TokenPrice >= decimals_mcap * supply_mcap) %>% nrow()

nrow(statusnetwork)
nrow(statusnetworkFiltered)
statusnetwork %>% filter(TokenPrice >= decimals_statusnetwork * supply_statusnetwork) %>% nrow()

nrow(bnb)
nrow(bnbFiltered)
bnb %>% filter(TokenPrice >= decimals_bnb * supply_bnb) %>% nrow()
```
##End Preprocessing.

###buying-selling distribution
###the fisrt column has the person selling token
###the second column has the person buying token. 
###We get the distribution
```{r}
mcap_users <- mcapFiltered[,1:2]
mcap_sorted_users <- mcap_users %>% filter(SellerInfo <= BuyerInfo)
mcap_users_to_swap <- mcap_users %>% filter(SellerInfo > BuyerInfo)
mcap_users_to_swap[ , c(1,2)] <- mcap_users_to_swap[ , c(2,1)]
mcap_sorted_users <- merge(mcap_sorted_users, mcap_users_to_swap)
mcap.distribution <- mcap_sorted_users %>% group_by(.dots = c("SellerInfo", "BuyerInfo")) %>% count() %>% ungroup
nrow(mcap.distribution)
```

```{r}
statusnetwork_users <- statusnetworkFiltered[,1:2]
statusnetwork_sorted_users <- statusnetwork_users %>% filter(SellerInfo <= BuyerInfo)
statusnetwork_users_to_swap <- statusnetwork_users %>% filter(SellerInfo > BuyerInfo)
statusnetwork_users_to_swap[ , c(1,2)] <- statusnetwork_users_to_swap[ , c(2,1)]
statusnetwork_sorted_users <- merge(statusnetwork_sorted_users, statusnetwork_users_to_swap)
statusnetwork.distribution <-statusnetwork_sorted_users %>% group_by(.dots = c("SellerInfo", "BuyerInfo")) %>% count() %>% ungroup
nrow(statusnetwork.distribution)
```

```{r}
bnb_users <- bnbFiltered[,1:2]
bnb_sorted_users <- bnb_users %>% filter(SellerInfo <= BuyerInfo)
bnb_users_to_swap <- bnb_users %>% filter(SellerInfo > BuyerInfo)
bnb_users_to_swap[ , c(1,2)] <- bnb_users_to_swap[ , c(2,1)]
bnb_sorted_users <- merge(bnb_sorted_users, bnb_users_to_swap)
bnb.distribution <- bnb_sorted_users %>% group_by(.dots = c("SellerInfo", "BuyerInfo")) %>% count() %>% ungroup
nrow(bnb.distribution)
```

##Total No of Buyer-Seller pairs in each tokenfile.
```{r}
nrow(mcap.distribution)
nrow(statusnetwork.distribution)
nrow(bnb.distribution)
```
```{r}
mcap.distribution<- mcap.distribution %>% filter(n > 3 & n < 300)
statusnetwork.distribution<-statusnetwork.distribution %>% filter(n > 3 & n < 300)
bnb.distribution<- bnb.distribution %>% filter(n > 3 & n < 300)
```

###finding best distribution
###fitdistrplus is a library we have used that to plot the graph for all distributions
###(exp,gamma,geometric,log,lnorm,nbinom,norm,pois,unif,weibull ) and
###finding the best distribution and estimates best parameters.
```{r}
fit.gamma.mcap <- fitdist(mcap.distribution$n, 'gamma',lower = c(0, 0), start = list(scale = 1, shape = 1))
fit.log.mcap <- fitdist(mcap.distribution$n, 'logis') 
fit.lnorm.mcap <- fitdist(mcap.distribution$n, 'lnorm') 
fit.nbinom.mcap <- fitdist(mcap.distribution$n, 'nbinom') 
fit.norm.mcap <- fitdist(mcap.distribution$n, 'norm') 
fit.unif.mcap <- fitdist(mcap.distribution$n, 'unif') 
fit.weibull.mcap <- fitdist(mcap.distribution$n, 'weibull')
```

```{r}
gofstat(list(fit.weibull.mcap, fit.gamma.mcap, fit.lnorm.mcap,
              fit.log.mcap, fit.nbinom.mcap, fit.norm.mcap, fit.unif.mcap))
```

```{r}
hist(mcap.distribution$n, pch=20, breaks=25, prob=TRUE, main="")

curve(dnorm(x, fit.gamma.mcap$estimate[1], fit.gamma.mcap$estimate[2]), col="red", lwd=2, add=T)
curve(dnorm(x, fit.log.mcap$estimate[1], fit.log.mcap$estimate[2]), col="orange", lwd=2, add=T)
curve(dnorm(x, fit.lnorm.mcap$estimate[1], fit.lnorm.mcap$estimate[2]), col="black", lwd=2, add=T)
curve(dnorm(x, fit.nbinom.mcap$estimate[1], fit.nbinom.mcap$estimate[2]), col="blue", lwd=2, add=T)
curve(dnorm(x, fit.norm.mcap$estimate[1], fit.norm.mcap$estimate[2]), col="pink", lwd=2, add=T)
curve(dnorm(x, fit.unif.mcap$estimate[1], fit.unif.mcap$estimate[2]), col="green", lwd=2, add=T)
curve(dnorm(x, fit.weibull.mcap$estimate[1], fit.weibull.mcap$estimate[2]), col="brown", lwd=2, add=T)
```

```{r}
fit.gamma.statusnetwork <- fitdist(statusnetwork.distribution$n, 'gamma',lower = c(0, 0), start = list(scale = 1, shape = 1))
fit.log.statusnetwork <- fitdist(statusnetwork.distribution$n, 'logis') 
fit.lnorm.statusnetwork <- fitdist(statusnetwork.distribution$n, 'lnorm') 
fit.nbinom.statusnetwork <- fitdist(statusnetwork.distribution$n, 'nbinom') 
fit.norm.statusnetwork <- fitdist(statusnetwork.distribution$n, 'norm') 
fit.unif.statusnetwork <- fitdist(statusnetwork.distribution$n, 'unif') 
fit.weibull.statusnetwork <- fitdist(statusnetwork.distribution$n, 'weibull')
```

```{r}
gofstat(list(fit.weibull.statusnetwork, fit.gamma.statusnetwork, fit.lnorm.statusnetwork,
              fit.log.statusnetwork, fit.nbinom.statusnetwork, fit.norm.statusnetwork,  fit.unif.statusnetwork ))
```
```{r}
hist(mcap.distribution$n, pch=20, breaks=25, prob=TRUE, main="")

curve(dnorm(x, fit.gamma.statusnetwork$estimate[1], fit.gamma.statusnetwork$estimate[2]), col="red", lwd=2, add=T)
curve(dnorm(x, fit.log.statusnetwork$estimate[1], fit.log.statusnetwork$estimate[2]), col="orange", lwd=2, add=T)
curve(dnorm(x, fit.lnorm.statusnetwork$estimate[1], fit.lnorm.statusnetwork$estimate[2]), col="black", lwd=2, add=T)
curve(dnorm(x, fit.nbinom.statusnetwork$estimate[1], fit.nbinom.statusnetwork$estimate[2]), col="blue", lwd=2, add=T)
curve(dnorm(x, fit.norm.statusnetwork$estimate[1], fit.norm.statusnetwork$estimate[2]), col="pink", lwd=2, add=T)
curve(dnorm(x, fit.unif.statusnetwork$estimate[1], fit.unif.statusnetwork$estimate[2]), col="green", lwd=2, add=T)
curve(dnorm(x, fit.weibull.statusnetwork$estimate[1], fit.weibull.statusnetwork$estimate[2]), col="brown", lwd=2, add=T)
```

```{r}
fit.gamma.bnb <- fitdist(bnb.distribution$n, 'gamma',lower = c(0, 0), start = list(scale = 1, shape = 1))
fit.log.bnb <- fitdist(bnb.distribution$n, 'logis') 
fit.lnorm.bnb <- fitdist(bnb.distribution$n, 'lnorm') 
fit.nbinom.bnb <- fitdist(bnb.distribution$n, 'nbinom') 
fit.norm.bnb <- fitdist(bnb.distribution$n, 'norm') 
fit.unif.bnb <- fitdist(bnb.distribution$n, 'unif') 
fit.weibull.bnb <- fitdist(bnb.distribution$n, 'weibull')
```

```{r}
gofstat(list(fit.weibull.bnb, fit.gamma.bnb, fit.lnorm.bnb,
              fit.log.bnb, fit.nbinom.bnb, fit.norm.bnb, fit.unif.bnb))
```

```{r}
hist(bnb.distribution$n, pch=20, breaks=25, prob=TRUE, main="")

curve(dnorm(x, fit.gamma.bnb$estimate[1], fit.gamma.bnb$estimate[2]), col="red", lwd=2, add=T)
curve(dnorm(x, fit.log.bnb$estimate[1], fit.log.bnb$estimate[2]), col="orange", lwd=2, add=T)
curve(dnorm(x, fit.lnorm.bnb$estimate[1], fit.lnorm.bnb$estimate[2]), col="black", lwd=2, add=T)
curve(dnorm(x, fit.nbinom.bnb$estimate[1], fit.nbinom.bnb$estimate[2]), col="blue", lwd=2, add=T)
curve(dnorm(x, fit.norm.bnb$estimate[1], fit.norm.bnb$estimate[2]), col="pink", lwd=2, add=T)
curve(dnorm(x, fit.unif.bnb$estimate[1], fit.unif.bnb$estimate[2]), col="green", lwd=2, add=T)
curve(dnorm(x, fit.weibull.bnb$estimate[1], fit.weibull.bnb$estimate[2]), col="brown", lwd=2, add=T)
```

##From the above statistics and graphs
##LNorm is the best distribution
##Estimated parameters are summarized below

```{r}
summary(fit.lnorm.mcap)
summary(fit.lnorm.statusnetwork)
summary(fit.lnorm.bnb)
```


#Question-2

#This question is similar to the first question. You will find the most active buyers and sellers in each of your three token network, and track them in other tokens. Develop a regression model where “buys” of the top K buyers (by number of buys or amount of buys) are regressors, and token price is the outcome. Determine a K value to have the best regression results. This means that you will develop three regression models for three tokens, and K can be different for each model.

##reading tokenprices file

```{r}
mcapPrice = read.table(file="mcap", header=T,sep="\t")
statusnetworkPrice = read.table(file="statusnetwork", header=T,sep="\t")
bnbPrice = read.table(file="bnb.csv", header=T,sep=",")
```

```{R}
colNames <- c("DATE","Open","High","Low", "Close" ,"Volume","MarketCap")
colnames(mcapPrice) <- colNames
colnames(statusnetworkPrice) <- colNames
colnames(bnbPrice) <- colNames
```


##reading tokenGraph file
```{r}
mcap <-read.table('networkmcapTX.txt', sep=" ")
statusnetwork <- read.table('networkstatusnetworkTX.txt', sep=" ")
bnb <- read.table('networkbnbTX.txt', sep=" ")
```

##naming columns for tokenGraph file
```{r}
names(mcap) <- c('SellerInfo', 'BuyerInfo', 'TimeStamp', 'TokenPrice')
names(statusnetwork) <- c('SellerInfo', 'BuyerInfo', 'TimeStamp', 'TokenPrice')
names(bnb) <- c('SellerInfo', 'BuyerInfo', 'TimeStamp', 'TokenPrice')
```

```{r}
mcap$DATE <- format(as.Date(as.POSIXct(as.numeric(as.character(mcap$TimeStamp)),origin="1970/01/01",tz="GMT"), tz="GMT"), "%m/%d/%Y")
statusnetwork$DATE <- format(as.Date(as.POSIXct(as.numeric(as.character(statusnetwork$TimeStamp)),origin="1970/01/01",tz="GMT"), tz="GMT"), "%m/%d/%Y")
bnb$DATE <- format(as.Date(as.POSIXct(as.numeric(as.character(bnb$TimeStamp)),origin="1970/01/01",tz="GMT"), tz="GMT"), "%m/%d/%Y")
```


```{r}
supply_mcap <- 100000000
supply_statusnetwork <- 6804870174.8781
supply_bnb <- 183345602.24249
decimals_mcap <- 10^8
decimals_statusnetwork <- 10^18
decimals_bnb <- 10^18
```


```{r}
mcapFiltered <- mcap %>% filter(TokenPrice < decimals_mcap* supply_mcap)
statusnetworkFiltered <- statusnetwork %>% filter(TokenPrice < decimals_statusnetwork * supply_statusnetwork)
bnbFiltered <- bnb %>% filter(TokenPrice < decimals_bnb* supply_bnb)
```

```{r}
mcap.distribution <- mcapFiltered %>% group_by(BuyerInfo) %>% summarise(n = n()) %>% ungroup
statusnetwork.distribution <- statusnetworkFiltered %>% group_by(BuyerInfo) %>% summarise(n = n()) %>% ungroup
bnb.distribution <- bnbFiltered %>% group_by(BuyerInfo) %>% summarise(n = n()) %>% ungroup
```

```{r}
mcaptopbuyerssorted <- mcap.distribution[order(mcap.distribution$n, decreasing = TRUE),] 
statusnetworktopbuyerssorted <- statusnetwork.distribution[order(statusnetwork.distribution$n, decreasing = TRUE),]
bnbtopbuyerssorted <- bnb.distribution[order(bnb.distribution$n, decreasing = TRUE),] 
```

```{r}
mcaptop100buys <- head(mcaptopbuyerssorted,100)
statusnetworktop100buys <- head(statusnetworktopbuyerssorted,100)
bnbtop100buys <- head(bnbtopbuyerssorted,100)
```

```{r}
mcapmergeboth <- merge(mcapFiltered,mcapPrice,by="DATE")
statusnetworkmergeboth <- merge(statusnetworkFiltered,statusnetworkPrice,by="DATE")
bnbmergeboth <- merge(bnbFiltered,mcapPrice,by="DATE")
```
```{r}
mcapmergeboth %>% group_by(mcapmergeboth$BuyerInfo)
statusnetworkmergeboth %>% group_by(statusnetworkmergeboth$BuyerInfo)
bnbmergeboth %>% group_by(bnbmergeboth$BuyerInfo)
```

```{r}
mcapmergebybuyerid <- merge(mcaptop100buys,mcapmergeboth,by="BuyerInfo")
statusnetworkmergebybuyerid <- merge(statusnetworktop100buys,statusnetworkmergeboth,by="BuyerInfo")
bnbmergebybuyerid <- merge(bnbtop100buys,bnbmergeboth,by="BuyerInfo")
```

```{r}
mcapaggamount <- aggregate(mcapmergebybuyerid$TokenPrice, by=list(mcapmergebybuyerid$DATE),sum)
statusnetworkaggamount <- aggregate(statusnetworkmergebybuyerid$TokenPrice, by=list(statusnetworkmergebybuyerid$DATE),sum)
bnbaggamount <- aggregate(bnbmergebybuyerid$TokenPrice, by=list(bnbmergebybuyerid$DATE),sum)
```

```{r}
names(mcapaggamount) <- c("DATE","AGGREGATEAMOUNT")
names(statusnetworkaggamount) <- c("DATE","AGGREGATEAMOUNT")
names(bnbaggamount) <- c("DATE","AGGREGATEAMOUNT")
```

```{r}
mcapfinalmerge <- merge(mcapPrice,mcapaggamount,by="DATE")
statusnetworkfinalmerge <- merge(statusnetworkPrice,statusnetworkaggamount,by="DATE")
bnbfinalmerge <- merge(bnbPrice,bnbaggamount,by="DATE")
```

```{r}
cor(mcapfinalmerge$Close,mcapfinalmerge$AGGREGATEAMOUNT)
cor(statusnetworkfinalmerge$Close,statusnetworkfinalmerge$AGGREGATEAMOUNT)
cor(bnbfinalmerge$Close,bnbfinalmerge$AGGREGATEAMOUNT)
```

```{r}
scatter.smooth(x=mcapfinalmerge$AGGREGATEAMOUNT, y=mcapfinalmerge$Close, main="TokenPrice ~ Close")
scatter.smooth(x=statusnetworkfinalmerge$AGGREGATEAMOUNT, y=statusnetworkfinalmerge$Close, main="TokenPrice ~ Close")
scatter.smooth(x=bnbfinalmerge$AGGREGATEAMOUNT, y=bnbfinalmerge$Close, main="TokenPrice ~ Close")
```

```{r}
mcapr <- lm(mcapfinalmerge$Close~mcapfinalmerge$AGGREGATEAMOUNT)
statusnetworkr <- lm(statusnetworkfinalmerge$Close~statusnetworkfinalmerge$AGGREGATEAMOUNT)
bnbr <- lm(bnbfinalmerge$Close~bnbfinalmerge$AGGREGATEAMOUNT)
```

```{r}
summary(mcapr)
summary(statusnetworkr)
summary(bnbr)

```

```{r}
mcaplmmod <- lm(mcapfinalmerge$Close ~ mcapfinalmerge$AGGREGATEAMOUNT)
statusnetworklmmod <- lm(statusnetworkfinalmerge$Close ~ statusnetworkfinalmerge$AGGREGATEAMOUNT)
bnblmmod <- lm(bnbfinalmerge$Close ~ bnbfinalmerge$AGGREGATEAMOUNT)
```

```{r}
print(mcaplmmod)
print(statusnetworklmmod)
print(bnblmmod)
```


